%! Author = Saeid Yazdani
%! Date = 5/14/2023


\chapter{Towards Safe and Reliable Electronic Systems}
\label{ch:towards-safe-reliable-systems}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Introduction}
\label{sec:ch1-introduction}

\subsection{The Intent}
\label{subsec:theintent}

Power requirements of modern electronic components and integrated circuits are
becoming more sophisticated with each new generation, thus pushing conventional
\acp{ATE} beyond their design limits.

Fast programmable power supplies are essential instruments for powering \acp{DUT}
and apply test patterns.
Therefore, test- and measurement-grade power supplies for qualification and
reliability testing of electronic components must deliver precise test waveforms
to devices under test to solve given test requirements.

This work is dedicated to investigations on \ac{ATE}
environments to identify limiting factors and bottlenecks.
Based on the findings, a proposal for power supply design and optimization of
control loop schemes in ATE \acp{SMU} by implementing a modern digital-oriented
control loop is made.
As a result, a prototype single-channel \ac{SMU} was developed as a test vehicle
for the proposed control loop schemes.

The research phase analyzes trends in the reliability of discrete electronic
components, semiconductors, and electronic systems and their relationship to
test and verification equipment to determine shortcomings and bottlenecks.
The implementation phase focuses on real-world solutions to improve test systems
and reduce limitations in the current generation of \acp{ATE}.

An \ac{ATE} offers an array of \acp{SMU} or \acp{DPS} (called channels),
operated and synchronized from a central supervising processor unit and
software.
Therefore, the proposed concept can be applied to larger and more
complex \acp{ATE}.

\subsection{The Importance of Testing}
\label{subsec:importance-testing}

The \ac{IEC} standard 1508~\autocite{SIL1508} defines a range that corresponds
to the safety-criticality of systems, as shown in \autoref{tab:sil-targets}.
According to these defined levels, a computer board designed to monitor and
regulate oxygen levels in a submarine will be at \textit{Level 4}.
In contrast, \textit{Level 1} represents systems where a failure is less likely
to result in a fatal incident, such as a temperature control system of a
household-grade fridge.

\begin{table}[h] % [h1] Causes the table be positioned within the text
    \resizebox{\textwidth}{!}{% Limit table size to text with by reducing font
        \centering
        \begin{tabular}{M{20mm}|P{50mm}|P{50mm}}

            \toprule

            \textbf{Level} &
            ~~~\textbf{Demand Mode}\newline \small{Probability of failure to perform its design function on demand} &
            ~~\textbf{Continuous Mode}\newline \small{Probability of a dangerous failure per year} \\

            \midrule

            % Row for level 4
            \textbf{4} &
            $>={10^{-5}}$ to $<{10^{-4}}$ &
            $>={10^{-5}}$ to $<{10^{-4}}$ \\
            \midrule

            % Row for level 3
            \textbf{3} &
            $>={10^{-4}}$ to $<{10^{-3}}$ &
            $>={10^{-4}}$ to $<{10^{-3}}$ \\

            \midrule

            % Row for level 2
            \textbf{2} &
            $>={10^{-3}}$ to $<{10^{-2}}$ &
            $>={10^{-3}}$ to $<{10^{-2}}$ \\

            \midrule

            % Row for level 1
            \textbf{1} &
            $>={10^{-2}}$ to $<{10^{-1}}$ &
            $>={10^{-2}}$ to $<{10^{-1}}$ % This was the last row

        \end{tabular}
    }% End resize to box
    \caption[\ac{SIL}]{\ac{SIL} Target failure measures introduced in
    IEC 1508 standard~\autocite{SIL1508}}
    \label{tab:sil-targets}
\end{table}

A system usually does not fail as a whole.
The failure starts within a building block of the system, and the failure in the
building block traces back to one or more discrete or integrated components.

Zooming into safety-critical systems at component level, the issue will become
more intriguing.
For example, if a device enters a latch-up state in an autopilot computer of an
airplane, this would lead to a fatal crash if no redundancy were available.

A list of what could go wrong with each passive and active component is long and
never complete.
The only way to ensure error-free components in a building block is to test
every component with proper test patterns using precise test equipment.

This stresses the importance of testing and qualification of components:
Excellent \acp{PSU} must be installed at the core of the test equipment, which
is vital for correctly evaluating the failure rate of components.

\input{chapter_one/history-elec-failures/content}

\input{chapter_one/design-and-test-challenges/content}

\input{chapter_one/reli_safe_and_secu/content}

\input{chapter_one/product_lifecycle/content}

\input{chapter_one/work_outline/content}

%\input{chapter_one/test_equipment_role_in_industry/content}

%\input{chapter_one/review_control_theory/content}

%\input{chapter_one/control-loop-in-psu/content}

%\input{chapter_one/compare-analog-digital-loops/content}

%\input{chapter_one/psu_performance_limiting_factors/content}
