%! Author = Saeid Yazdani
%! Date = 5/18/2023

%\addcontentsline{toc}{section}{\bf Abstract (EN)}

\begin{flushleft}
%  \thispagestyle{empty}
    \section*{\textbf{Abstract}}
    \justifying
    \vskip 1cm

    Electrical and functional testing and qualification are vital steps in
    the production cycle of semiconductor devices. Reputable manufacturers
    rely heavily on \acs{ATE} to perform various tests and qualifications on
    their products during and after fabrication to ensure the delivery of
    safe and reliable products to the market.

    The ever-increasing complexity of semiconductors and advancements in
    fabrication processes call for equally developed test and measurement
    equipment capable of stimulating and capturing the smallest (in the case
    of integrated circuits) and largest (in the case of power components)
    voltages and currents with maximum precision and accuracy.

    Power supply modules of traditional ATE systems mainly depend on analog
    control loops to keep test signals within required envelopes.
    These analog control loops have known limitations that may only
    partially satisfy modern semiconductor test and qualification
    requirements.

    These limitations include, but are not limited to, large component
    count, tendency to overshoot or undershoot in response to load
    variations and the need for additional circuitry for implementing
    supervisory functions such as overvoltage or overcurrent monitoring.

    This work studies the limitations of traditional control loops in test
    and measurement equipment and proposes a hybrid analog-digital control
    scheme to overcome the shortcomings of purely analog
    systems.

    A four-quadrant \SI{\pm320}{\volt} \acs{DPS} prototype
    capable of delivering up to \SI{2}{\ampere} continuous current
    and up to \SI{10}{\ampere} in pulse-mode is then developed and
    evaluated in a series of real-world scenarios where stable power delivery
    for \acs{DUT} and precise and accurate test signals for
    characterization and verification of such \acs{DUT}s are needed.


    \vskip 0.45cm
    \section*{\textbf{Keywords}}
    {\setstretch{1.0}
    Automated Test Equipment, Digital, Analog, Control Loop, Test, Qualification,
    Safety, Reliability, Verification, Measurement, Semiconductor, Power Supply,
    Integrated Circuit
    \par}

\end{flushleft}
