%! Author = Saeid Yazdani
%! Date = 5/18/2023

%\addcontentsline{toc}{section}{\bf Acknowledgement}

\begin{flushleft}
%  \thispagestyle{empty}
    \section*{\textbf{Acknowledgement}}
    \justifying
    \vskip 1cm

    \noindent
    I would like to express my deepest gratitude to \VARgutachterOne~
    for granting me the opportunity to work on this project and for his
    unwavering support throughout the research and implementation phases.
    His guidance made this work possible.

    \noindent
    I am also deeply thankful to \VARgutachterThree~ for his invaluable
    assistance and feedback on the technical aspects of the prototypes
    developed in this work.

    \noindent
    A special thanks to \VARgutachterFour~for providing insightful
    feedback and thorough reviews on the academic aspects of this thesis.

    \noindent
    I am particularly grateful to \VARgutachterTwo~ for agreeing to serve
    as the second official referee.
    His careful evaluation and constructive suggestions have greatly
    improved the quality of this work.

    \noindent
    Many thanks to my colleagues at the
    Circuit and System Design Chair of Chemnitz University of Technology and
    at \VARindustrypartner~ for their support
    and encouragement throughout this journey.

    \noindent
    I would like to express my thanks to Mr. Eik Arnold, my manager
    at the time in Rohde \& Schwarz Chemnitz, for his support
    and encouragement to finalize this work after facing multiple challenges
    during the coronavirus pandemic.

    \noindent
    Last but not least, I would like to sincerely thank my family for their
    patience and understanding throughout this journey.

\end{flushleft}
