%! Author = Saeid Yazdani
%! Date = 4/9/2024

\chapter{\acs{ATE} Power Supply Diagnostics}
\label{ch:diagnostics}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Introduction}
\label{sec:ch-diagnostics-introduction}

In the previous chapters, the contributing elements to integrity
and health of test signals and quality of the power delivered at the \ac{DUT}
site were evaluated.

We strictly enforce a \emph{Full Test-Setup Analysis} using advanced
socket-integrated analysis tools (\ac{VDUT} analysis).
During the test program execution, a test engineer must be able to
understand all parasitic effects that originate from load board subtleties
like non-equal length design, high-impedance \ac{DUT} support lines, etc.

The performance of the \acs{ATE} \acs{DPS} units were evaluated by performing
direct measurement on the existing load board and \ac{VDUT} in the socket.
This assessment revealed that state-of-the-art \ac{DPS} designs have
shortcomings in their control mechanism and that they are not designed to
guarantee range switching without massive errors (there is a considerable
sensitivity to sequencing and timing within the firmware code).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapter_five/diagnostics/content}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapter_five/capacitive_loads/content}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapter_five/current_limit/content}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapter_five/ganged_mode_dps/content}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{chapter_five/dps_control_loop/content}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}
\label{sec:diagnostics-conclusion}

In this chapter, we examined the factors causing problems with \ac{ATE}'s
\ac{DPS} units.
Some of the issues are caused by the load board design, but most are due to the
\ac{DPS} units struggling with capacitive loads and higher current demands.

Major glitches and unwanted voltages at the DUT site point to issues with
synchronizing multiple DPS channels, which is necessary for providing the
required current.

The analog control loop of the DPS is a major limitation.
Unlike digital systems, analog loops cannot be easily adjusted for each
\ac{DUT}'s characteristics to improve response times and compensate for load
conditions.
Analog loops are more prone to noise and drift, affecting performance and
stability.
They lack the precision and flexibility of digital systems, which can offer
more consistent operation and better performance through software adjustments.

Switching to digital control loops in DPS units could solve many of the
discussed problems.
Digital control offers advanced tools for real-time monitoring and
troubleshooting, making it easier to maintain and improve performance and are
more scalable and adaptable, better suited to handle the varying demands
of \ac{ATE} systems.

Furthermore, it is crucial to develop a solution with a sufficient current
output rating, eliminating the need for ganging configurations.
Avoiding ganging will reduce the synchronization and timing issues
related to relay switching and improve the overall reliability and simplicity
of the system.

In conclusion, to improve the reliability and performance of \ac{ATE} power
supplies, it is important to consider moving from analog to digital control
loops.
Additionally, we need to ensure that power supplies have enough current
output to avoid the complications of ganging.
This change would allow for more precise, adaptable, and stable power delivery,
improving the accuracy of test signals at the \ac{DUT} site.

In the following chapters, we will explore the concept of designing a hybrid
analog-digital \ac{DPS}, focusing on a time-variant control loop.
The discussion will include an evaluation of this approach and a detailed
insight into the implementation of a prototype.
This proposed solution aims to combine the strengths of both analog and
digital systems, potentially offering enhanced performance and
flexibility in \ac{ATE} power supplies.
